Decentralized Data Marketplace to Enable Trusted Machine Economy

### 2019-08-27 paper.tex

\subsubsection{Registrar}
Registrar is responsible for creating a Registration Contract, which preserves a lookup table of participants, and adding new data providers, consumers and brokers to the decentralized data marketplace.

\subsubsection{Data Provider}
Data providers, who generate and preserve IoT data, are willing to sell sensing data to consumers. They decide the subscription period, subscription price, data type, sampling frequency. Afterward, they can launch the product on the decentralized data marketplace. Next, they collect raw data with their sensors and send it to the broker who will assist in uploading it to the network. A MAM channel\cite{MAM} is used to store  encrypted data stream.

>>>>

\subsubsection{Registrar}
Registrar is responsible for creating a Registration Contract, which maintains a lookup table of participants, and adding new data providers, consumers and brokers to the decentralized data marketplace.

\subsubsection{Data Provider}
Data providers, who generate and preserve IoT data, are willing to sell sensing data to consumers. They decide the subscription period, subscription price, data type, sampling frequency. Afterward, they can launch the product on the decentralized data marketplace. Next, they collect raw data with their sensors and send to the broker who assists in uploading data to the network. An MAM channel\cite{MAM} is used to store encrypted data stream.
